\documentclass[sigconf]{acmart}

\usepackage{hyperref}

\usepackage{endfloat}
\renewcommand{\efloatseparator}{\mbox{}} % no new page between figures

\usepackage{booktabs} % For formal tables

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

\begin{document}
\title{Big Data and Analytics in Block Chain}


\author{Ashok Kuppuraj}
\orcid{1234-5678-9012}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{}
  \city{Bloomington} 
  \state{Indiana} 
  \postcode{43017-6221}
}
\email{akuppura@iu.edu}


% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{G. v. Laszewski}


\begin{abstract}
This paper describes an idea how Big data and its technologies helps in augmenting or improving the current Block chain technology and overcome one of the problems around it like non-real time transaction time and .
\end{abstract}

\keywords{Big Data, Block Chain i523}


\maketitle

\section{Introduction}
The Objective of this project to concur the abilities of the two broad topics in the current technology world, the two B's , Big Data and Block Chain. Block chain and Bigdata both are still a evolving technologies, which gives me enough opportunity to explore and invent new conepts for its own good. As these are still evolving, we can leverage ones solution on the other.  To leverage eaach ones problems and solutions, we must first identify the similarities in the two frameworks and how these similarities are related and what solution we are going to choose. 

 \cite{editor00}.

\section{What is Big Data}


\section{Conclusion}

Put here an conclusion. Conlcusions and abstracts must not have any
citations in the section.


\begin{acks}

  The authors would like to thank Dr. Gregor von Laszewski for his
  support and suggestions to write this paper.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 

\end{document}
